\subsubsection{Attributed grammar}
\input{content/attributed}

\subsubsection{New examples}
\input{content/example}
\input{content/dining}
\input{content/account}

\subsubsection{Feature}
During this period, various features have been added to the tool:
\begin{itemize}  
    \item \textbf{Improved over-approximation in the global view}:  
    If, during computation, the value of some data is lost, the tool now  
    uses the \texttt{ANY} constant to indicate that it can represent any kind  
    of data. If a message is exchanged with \texttt{ANY} as its content, it  
    will match every possible receive branch, ensuring a more comprehensive  
    analysis.  
    
    \item \textbf{Basic value passing in the local view}:  
    The tool can now correctly parse programs where values are passed as  
    arguments to functions, allowing for a more accurate representation of  
    data flow between processes.  
    
    \item \textbf{Enhanced error handling}:  
    The tool is now more resilient to unexpected errors, reducing the  
    likelihood of crashes and ensuring that it provides meaningful output in  
    most cases, even when encountering invalid input.  
    
    \item \textbf{Improved CLI experience}:  
    A new library has been integrated for command-line argument management,  
    making the CLI more robust and user-friendly, with better parsing of  
    parameters and improved error messages.  

    \item \textbf{Improved testing environment and benchmark generation}:  
    The tool now produces useful benchmarking information, which is processed  
    by a dedicated Python script. This script collects and analyzes the data  
    to generate meaningful performance benchmarks. Additionally, if the  
    \texttt{correct\_gv.dot} file is present—containing the expected global  
    view—the script performs an automatic correctness check. This feature  
    lays the groundwork for more expressive and rigorous testing in the future,  
    enabling better validation of the tool's accuracy and performance across  
    different scenarios.  

\end{itemize}

\subsubsection{Bug Fix}
All of these improvements are made within the global view module:  
\begin{itemize}  
    \item \textbf{Fixed a bug causing false positive warnings}:  
    Resolved an issue where the tool incorrectly printed warnings about  
    failing to find the correct process during the emulation of a global view.  
    
    \item \textbf{Fixed a bug preventing full branch exploration}:  
    Addressed a problem that prevented the exploration of certain branches  
    during the global view emulation, ensuring a more comprehensive traversal  
    of all possible execution paths.  
    
    \item \textbf{Fixed a bug causing excessive duplicate branches}:  
    Corrected an issue where unnecessary duplicate branches were created  
    after receiving a message and defining a new variable. This fix improves  
    the accuracy of the global view by reducing redundant computations.  
\end{itemize}  


\subsubsection{Benchmarks}
\input{content/benchmarks}
